A forest is more than its trees: haplotypes and inferred ARGs

### 2024-12-16 paper/writeup.tex
minor merge fix
IBD note; closes #26

>>>>

\paragraph{IBD in ARGs}
The term ``identity by descent'' (IBD) is used to mean many different (but related) things,
and length distributions of shared IBD segments can be used for inference of recent demographic history
\citep[for instance,][]{alasadi2018estimating,ringbauer2017inferring,browning2015accurate}.
A commonly-used definition in the context of a given ARG says that
the two genomes share an IBD segment if each has inherited the segment from their common ancestor
along a single path \citep{ralph2013geography}.
Largely for computational reasons, this is the definition that is used in \tskit's
IBD-finding methods 
(by G.~Tsambos \citet{tskit}; see also \citet{tsambos2023link}).
However, many simulation and inference methods produce ARGs
as shown in \figref[A\&B]{fig:conceptual},
in which inheritance of a single segment is represented by more than one edge.
This means that the \texttt{ibd\_segments} method of \tskit{} will return shorter segments than it ought to.
However, applying our method of extending haplotypes
will remove this issue, and so should make returned IBD segments
more closely match those predicted by theory.
